---
title: "EMM CANTOS"
author: "Yi Li"
date: "24/09/2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(regmedint)
```

## 0. Data Source
Original paper: Vallurupalli M, MacFadyen JG, Glynn RJ, et al. Effects of Interleukin-1$\beta$ Inhibition on Incident Anemia: Exploratory Analyses From a Randomized Trial. Ann Intern Med. 2020;172(8):523. doi:10.7326/M19-2945

```{r}
setwd("/Users/yili/Desktop/_cantos_analyses/Anemia outcome")

anemia3 <- read.csv("~/Desktop/_cantos_analyses/Anemia outcome/anemia3.csv", header = FALSE)

colnames(anemia3) <- c("canakinumab", "age", "female", "base_logCRP", 
                       "chf", "htn", "dm", "egfrlo", "3mo_logCRP_100", 
                       "anemiaev", "anemiayrs"
                       )

anemia3$diff_logCRP <- anemia3$`3mo_logCRP_100`/100 - anemia3$base_logCRP
```

## 1. Variables
Treatment: canakinumab use (binary)

Mediator: change in log CRP (continuous)

Outcome: anemia (survival time)

Baseline confounders: age, sex, baseline log CRP, heart failure, hypertension, diabetes




```{r}
c_cond0_mean <- sapply(anemia3[, c("age", "female", "base_logCRP", 
                              "chf", "htn", "dm")], mean)
c_cond0_mean

# Condition on other non-EMM covariates:
# female = 0, chf (heart failure) = 0, htn (hyptertention) = 1
c_cond0 <- c(mean(anemia3$age), 0, mean(anemia3$base_logCRP), 0, 1, 0)
c_cond0

cvar = c("age", "female", "base_logCRP", 
         "chf", "htn", "dm")
```

## 2. Mediation analyses
### (1) No Effect modification by any covariates
```{r}
fit0.0 <- regmedint(data = anemia3,
                    yvar = "anemiayrs",
                    eventvar = "anemiaev",
                    avar = "canakinumab",
                    mvar = "diff_logCRP",
                    cvar = cvar,
                    ## EMM
                    emm_ac_mreg = NULL,
                    emm_ac_yreg = NULL,
                    emm_mc_yreg = NULL,
                    ##
                    mreg = "linear",
                    yreg = "survAFT_weibull",
                    interaction = TRUE,
                    casecontrol = FALSE,
                    a0 = 0,
                    a1 = 1,
                    m_cde = mean(anemia3$diff_logCRP),
                    c_cond = c_cond0)
summary(fit0.0)
```



### (2) Effect modification by baseline logCRP in mediator model, and age & diabetes in outcome model 
### a. Specify low and high risk groups' covariate levels
```{r}
c_cond_low_all <- c_cond_high_all <- c_cond0
c_cond_low_all[c(1, 3, 6)] <- c(quantile(anemia3$age, 0.25), 
                                quantile(anemia3$base_logCRP, 0.25), 
                                0)
c_cond_high_all[c(1, 3, 6)] <- c(quantile(anemia3$age, 0.75), 
                                 quantile(anemia3$base_logCRP, 0.75), 
                                 1)

# c_cond_low_all
# c_cond_high_all
```

### b. Fit regmedint function
```{r}
fit1.1 <- regmedint(data = anemia3,
                    yvar = "anemiayrs",
                    eventvar = "anemiaev",
                    avar = "canakinumab",
                    mvar = "diff_logCRP",
                    cvar = cvar,
                    ## EMM
                    emm_ac_mreg = c("base_logCRP"),
                    emm_ac_yreg = NULL,
                    emm_mc_yreg = c("age", "dm"),
                    ##
                    mreg = "linear",
                    yreg = "survAFT_weibull",
                    interaction = TRUE,
                    casecontrol = FALSE,
                    a0 = 0,
                    a1 = 1,
                    m_cde = mean(anemia3$diff_logCRP),
                    c_cond = c_cond_low_all)

summary(fit1.1)

fit1.2 <- regmedint(data = anemia3,
                    yvar = "anemiayrs",
                    eventvar = "anemiaev",
                    avar = "canakinumab",
                    mvar = "diff_logCRP",
                    cvar = cvar,
                    ## EMM
                    emm_ac_mreg = c("base_logCRP"),
                    emm_ac_yreg = NULL,
                    emm_mc_yreg = c("age", "dm"),
                    ##
                    mreg = "linear",
                    yreg = "survAFT_weibull",
                    interaction = TRUE,
                    casecontrol = FALSE,
                    a0 = 0,
                    a1 = 1,
                    m_cde = mean(anemia3$diff_logCRP),
                    c_cond = c_cond_high_all)


summary(fit1.2)
```


